Why Real-World Subgraph Isomorphism is Easy, \\ and What This Means for Graph Databases

### 2017-07-24 paper/paper.tex
Abstract tweak

    When labels are introduced, as commonly seen in real-world applications and in graph databases,
    additional rich behaviour arises.  We show that when even the simplest constraint programming
    algorithms are used, all commonly used benchmark suites for evaluating graph database systems
    become trivial, and that existing notions of difficulty are based almost entirely upon
    unnecessarily poor performance from overly simplistic subgraph isomorphism algorithms. With this
    in mind, we demonstrate that the widely researched ``filter~/ verify'' indexing technique used in
    graph databases is a flawed design based upon a repeated misunderstanding of what makes subgraph
    isomorphism hard. We explain why filter~/ verify cannot be beneficial, even with harder
    instances than those currently used, when paired with any reasonable modern subgraph isomorphism
    algorithm.
\end{abstract}

>>>>

    When labels are introduced, as commonly seen in real-world applications and in graph databases,
    additional rich behaviour arises.  We show that when even the simplest constraint programming
    algorithms are used, all commonly used benchmark suites for evaluating graph database systems
    become trivial, and that existing notions of difficulty are based almost entirely upon
    unnecessarily poor performance from overly simplistic subgraph isomorphism algorithms. With this
    in mind, we demonstrate that the widely researched ``filter~/ verify'' indexing technique used in
    graph databases is a flawed design based upon a repeated misunderstanding of the empirical
    hardness of \NP-complete problems. We explain why filter~/ verify cannot be beneficial, even
    with harder instances than those currently used, when paired with any reasonable modern subgraph
    isomorphism algorithm.
\end{abstract}
